Distributed Multi-Heuristic A* (HAMSTAR)

### 2014-12-11 paper.tex
Expanded conclusion

@@

In this paper we outlined the details of a distributed version of the SMHA* algorithm. We detailed the structure of the algorithm, and presented experimental results comparing the performance of the algorithm while varying a number of parameters. We also compared its performance to the original SMHA* algorithm. Although we found that in the specific domain we tested on (the sliding tile puzzle) our distributed variant did not outperform the original algorithm, we provided evidence that our algorithm could outperform SMHA* in domains where heuristics are difficult to calculate, or in general where state expansion is expensive.
% TODO: Fill me in!

>>>>

We ultimately chose the broadcast model for our implementation due to the more balanced workload on the anchor. In fact, in the specific problem we analyzed (the sliding tile puzzle), using the one-on-one communication model was not a viable option; it would take longer for the anchor to process incoming states and send them out than it would for child nodes to expand new states.

@@

In this paper we outlined the details of a distributed version of the SMHA* algorithm. We detailed the structure of the algorithm, and presented experimental results comparing the performance of the algorithm while varying a number of parameters. We also compared its performance to the original SMHA* algorithm.

In the specific domain we tested on (the sliding tile puzzle) our distributed variant did not outperform the original algorithm. The culprit appears to be the excessive communication cost relative to the cost of expanding a state. We were partially able to mitigate this by using the broadcast model of communication, and by reducing the footprint of a communicated state by not recovering the backpointer until the end and by offloading the calculation of the anchor heuristic onto the child machines. Nevertheless, it appears more optimizations would be required in order to gain a significant benefit over vanilla SMHA*. One possibility is the use of asynchronous communication. Both of our communication models required the sender and receiver to be ready to communicate simultaneously. If one was ready before the other, then that machine would be blocked until the counterpart responded. Using asynchronous communication would eliminate the requirement that all machines cease work until all are ready, which becomes a more significant problem as the size of the distribution grows due to the possibility of slow outlier machines. This would also make the algorithm more robust to failure, since the algorithm could proceed even if one machine becomes unresponsive. The latest version of MPI (MPI 3.0) appears to include an asynchronous broadcast option that would accomplish something similar to this.

Although we found that in the specific domain we tested on (the sliding tile puzzle) our distributed variant did not outperform the original algorithm, we provided evidence that our algorithm could outperform SMHA* in domains where heuristics are difficult to calculate, or in general where state expansion is expensive.
